Hippocampal replay of experience at real world speeds

### 2021-05-13 Article.tex
Update on Overleaf.

The brain has the remarkable ability to store and retrieve representations of past events, allowing memories of the past to influence the future. These memory processes depend critically on the hippocampus, where rapid plasticity during an experience is thought to drive the initial encoding of events \citep{EichenbaumCanWeReconcile2014}. Subsequently, hippocampal "replay" of stored representations during both slow-wave sleep and periods of immobility during waking contributes to the longer term storage and updating of event memories in distributed hippocampal-neocortical circuits \citep{Franklandorganizationrecentremote2005, Joohippocampalsharpwave2018}. Experiences can take place over many seconds, minutes, hours or days, and to be useful in guiding behavior, memories of these events must be stored in such a way that they can be retrieved quickly to inform upcoming choices. Consistent with this need for rapid storage, hippocampal replay events can express time compressed representations of past experience, activating regions outside the hippocampus and presumably driving plasticity in those regions to promote memory storage \citep{CarrHippocampalreplayawake2011}.

@@

Our uncertainty stems in part from the dominant approaches used to identify the content of replay events. These approaches typically involve multiple steps and assumptions about the nature of replay, which are most commonly characterized using the standard "Bayesian" decoder. First, an encoding model is constructed based on spiking activity during movement, most often using only spikes that have been clustered as single units (putative single neurons). Then, a subset of SWRs or events with high activity levels are selected based on a threshold for event size chosen by the experimenter \citep{FosterReversereplaybehavioural2006, DibaForwardreversehippocampal2007a, KarlssonAwakereplayremote2009, StellaHippocampalReactivationRandom2019}. A decoding algorithm is then applied to the spikes within these events, yielding a set of position probability distributions for each time bin. Current approaches use either overlapping or non-overlapping time bins whose size is also chosen by the experimenter. Finally, the most commonly used approaches for detecting sequential replay involve fitting a line to the resulting set of probability distributions, which relies on the assumption that the representations progress at a constant speed \citep{FosterReversereplaybehavioural2006, DibaForwardreversehippocampal2007a, KarlssonAwakereplayremote2009}. A statistical test is then used to determine whether the line fit to the data is better than a line fit to shuffled versions of the data, where the shuffled version of the data represent an implicit definition of a "random" sequence.

@@

Recognizing the problems with the linear fit, several studies have moved away from the constant velocity assumption, using the most probable location at each time bin. For example, using this approach, \cite{PfeifferAutoassociativedynamicsgeneration2015} found that awake replays can alternate between representing a single location and sequential spatial trajectories. On the other hand, \cite{StellaHippocampalReactivationRandom2019} reported that replays during sleep are spatially continuous and follow Brownian diffusion dynamics. However, both methods still used large time bins and neither took into account the uncertainty of the decoded estimates, making it hard to identify the source of the different conclusions.

>>>>

The brain has the remarkable ability to store and retrieve representations of past events, allowing memories of the past to influence the future. These memory processes depend critically on the hippocampus, where rapid plasticity during an experience is thought to drive the initial encoding of events \citep{Eichenbaumconditioningconsciousrecollection2004}. Subsequently, hippocampal "replay" of stored representations during both slow-wave sleep and periods of immobility during waking contributes to the longer term storage and updating of event memories in distributed hippocampal-neocortical circuits \citep{Franklandorganizationrecentremote2005, Joohippocampalsharpwave2018}. Experiences can take place over many seconds, minutes, hours or days, and to be useful in guiding behavior, memories of these events must be stored in such a way that they can be retrieved quickly to inform upcoming choices. Consistent with this need for rapid storage, hippocampal replay events can express time compressed representations of past experience, activating regions outside the hippocampus and presumably driving plasticity in those regions to promote memory storage \citep{CarrHippocampalreplayawake2011}.

@@

Our uncertainty stems in part from the dominant approaches used to identify the content of replay events. These approaches typically involve multiple steps and assumptions about the nature of replay, which are most commonly characterized using the standard "Bayesian" decoder. First, an encoding model is constructed based on spiking activity during movement, most often using only spikes that have been clustered as single units (putative single neurons). Then, a subset of SWRs or events with high activity levels are selected based on a threshold for event size chosen by the experimenter \citep{FosterReversereplaybehavioural2006, DibaForwardreversehippocampal2007a, KarlssonAwakereplayremote2009, StellaHippocampalReactivationRandom2019}. A decoding algorithm is then applied to the spikes within these events, yielding a set of position probability distributions for each time bin. Current approaches use either overlapping or non-overlapping time bins whose size is also chosen by the experimenter. Finally, the most commonly used approaches for detecting sequential replay involve fitting a line to the resulting set of probability distributions, which relies on the assumption that the representations progress at a constant speed \citep{FosterReversereplaybehavioural2006, DibaForwardreversehippocampal2007a, KarlssonAwakereplayremote2009, TingleyRoutingHippocampalRipples2020, BhattaraiDistincteffectsreward2020, ShinDynamicsAwakeHippocampalPrefrontal2019, DrieuNestedsequenceshippocampal2018, OlafsdottirTaskDemandsPredict2017, TangHippocampalPrefrontalReactivationLearning2017, CarrTransientSlowGamma2012, DavidsonHippocampalReplayExtended2009, KarlssonAwakereplayremote2009}. A statistical test is then used to determine whether the line fit to the data is better than a line fit to shuffled versions of the data, where the shuffled version of the data represent an implicit definition of a "random" sequence.

@@

Recognizing the problems with the linear fit, several studies have moved away from the constant velocity assumption, using the most probable location at each time bin \citep{}. For example, using this approach, \cite{PfeifferAutoassociativedynamicsgeneration2015} found that awake replays can alternate between representing a single location and sequential spatial trajectories. On the other hand, \cite{StellaHippocampalReactivationRandom2019} reported that replays during sleep are spatially continuous and follow Brownian diffusion dynamics. However, both methods still used large time bins and neither took into account the uncertainty of the decoded estimates, making it hard to identify the source of the different conclusions.
